Reactive silver inks for antiviral, repellent medical textiles with ultrasonic bleach washing durability compared to silver nanoparticles

### 2022-01-20 Latex/Response Letter1.tex

\blue{
The text has been modified for 
clarity. On page 4, paragraph 2 the role of octadecylamine functionalized nano graphene oxide (nGO-ODA) is explained ``In this work, we demonstrate a nano-graphene oxide (nGO) that is coal-derived, 
as opposed to graphite-derived and is 
thus, cheaper and more realizable for large scale applications such as fabrics.The nGO is functionalized with long hydrocarbon chains from octadecylamine (ODA) to make  octadecylamine functionalized nano-graphene oxide (nGO-ODA). The ODA functional group adds a liquid repellent property to the nGO from low surface energy, hydrocarbon chains. nGO-ODA offers the advantage of simultaneous liquid repellency and viral inhibition properties compared to conventional GO or nitrogen doped GO, which only demonstrate virus inhibition."}

\blue{The role of PET, etched PET and etched PET-nGO-ODA is explained on page 8 paragraph 1 ``In this study, we use polyester (PET) as fabric material since it is commonly used for medical and healthcare applications such as gowns, scrubs and caps...Roughening the microfibers prior to coating renders the surface superhydrophobic once the nGO-ODA coating is added...The additon of nGO-ODA material lowers the overall surface energy and adds roughness at the nanoscale, important for repelling small scale (less than 600 nm) particulates.$^{29}$"}

\blue{The role of etched PET-nGO-ODA/PDMS is explained on page 16 paragraph 1``Since some of the nGO-ODA material on EPET-nGO samples can be removed from the fabric when subject to extended washing cycles with bleach, a thin layer of PDMS is applied to the fabric afterwards to improve the bleach wash durability by adding chemical resistance. The PDMS adds chemical resistance and durability so the treatment may be re-usable in bleach washing procedures."}

\item     In the preparation process 200mg of octadecylamine used in this work and in the XPS spectrum elemental analysis (Figure 1d) are also shows the minimum amount of addition of the amine group in the functionalization. At what measure the author fixed the particular concentration and justify with the experiment with concentration variation with the functionalization and concentration variation of the composite.

\blue{The ODA:nGO ratio for functionalization was chosen to be 2:1.  The following text has been added to the experimental information under Preparation of nGO-ODA ``A 2:1 ratio of ODA:nGO was observed to be the ideal ratio for a coating solution. At lower ratios, the solution aggregates in organic solvents and the graphene flakes are not fully functionalized. At larger ratios, the solution is mostly amines and too viscous for coating. The ratio was chosen based on observational experiments in the lab." }
%\commentPaul{Think more information in the text similar to the explanation here.}

\item     The authors reported the SEM image of the PET, EPET and EPET-nGO sample. Why the scale is deleted in the image? The author should report with the correct scale.

\blue{The scale was omitted by accident and now has been added.}

\item      In the figure 2C the FTIR spectrum of the different samples reported. But amine group vibration is not identified in the sample. The author have to justify the same with the clear explanation.

\blue{The following text was added to the end of page 9, last sentence, ``The amine group vibration from the GO-ODA can not be identified due to the dominant signal from the hydrocarbon groups of the polyester substrate."}

\item      The virus repellant property of the fabric have been tested and reported in the figure 4 and 6. What is the real property associated with the virus repulsion other than the phobicity. The author have to explain clearly.

\blue{Page 18 paragraph 2 has been modified ``The reduction of virus quantities from anti-virofouling comes from the stable Cassie-Baxter wetting state. In a stable Cassie-Baxter wetting state, the area of fabric contact for virus particles in liquid to contaminate the fabric surface is significantly less due to the trapped pockets of air.$^{11}$ The  combination of nanoroughness from the 2 dimensional graphene lattices and low surface energy from the ODA functional groups promote self-cleaning of extremely small (less than 600 nm) contaminants, such as viruses by reducing the area of contact.$^{29}$  The treated surface prevents liquid penetration and significantly reduces virus-to-surface contact area; therefore, less virus particles may attach to the surface. "}

\item    In the figure 6, the virus quantity have been reduced, which suggesting that the fabric have the virus resistance. Usually, viral resistance can be caused with the protein leakage or structural breakage. The author have to identify the mechanism of the viral resistance with essential proof.\\
\blue{This study focuses on the durabilitiy of the virus functionality on fabric. In our experiments, we observed that the textile coatings are antiviral from a combination of reducing viral adhesion to the surface and  
inhibiting virus infectivity.  
%virus inhibition of infectivity effect, where the infectivity of the virus is inhibited. This is just as useful as destroying the virus; however, the mechanism of the inhibition is beyond the scope of this work 
The reduction of virus infectivity was observed with the nGO-ODA material in PBS and on fabrics. 
%for HAdV5. to the surface appears to be dominant though as virus inhibition experiments demonstrated a reduction of HAdV5 by $0.88 \pm 0.64$ log$_{10}$
%compared to $1.8$ log$_{10}$
%with EPET-nGO/P samples.  
However, the mechanism of the inhibition is beyond the scope of this work and can be identified in future studies.  The literature has mentioned both mechanical damage and/or oxidative stress as antiviral mechanisms, but there is currently no consensus.} 
%\commentPaul{Why?  Explain what this would entail and why it is beyond the scope of this work.}
%and may be explained in future studies.} 
%\commentPaul{Not sure how we concluded this.  0.88 log is much smaller than 1.8 log?}
% The dominant property is anti-virofouling, though there is also some inhibition.}

%\blue{``Virus resistance" should be used in this case. Viral resistance to an agent is acquired over a period of time after exposure to the agent in which there is a decreased susceptibility over time. These viruses were never exposed to the agents prior to the assay and therefore resistance does not occur. We did observe a virus inhibition of infectivity effect, where the infectivity of the virus is inhibited. This is just as useful as destroying the virus; however, the mechanism of the inhibition is beyond the scope of this work and may be explained in future studies. The dominant property is anti-virofouling, though there is also some inhibition.}
%This effect is small and we conclude the dominant property occurring is anti-virofouling. }

\end{enumerate}

\blue{In addition to these changes, we have also made minor changes throughout the paper in order to improve its quality.}

\newpage

\textbf{Submitting Authors:}\\
%Sajad Haghanifar\\
%Benedum Hall, Room SB10 \\
%Pittsburgh, PA 15261\\
%Email:  \href{mailto:sah175@pitt.edu}{sah175@pitt.edu}\\
%Phone: (412) 499-0768
Anthony J. Galante\\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:ajg109@pitt.edu}{ajg109@pitt.edu}\\
Phone: (919) 757-4183\\

Brady C. Pilsbury \\
University of Pittsburgh \\
Department of Industrial Engineering \\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\

Kathleen A. Yates\\
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:kayates@pitt.edu}{kayates@pitt.edu}\\

Melbs LeMieux \\
Electroninks Inc \\ 
7901 East Riverside Drive, Bldg 1,Unit 150\\
Austin TX  78744 \\

Eric G. Romanowski\\
%\altaffiliation{A shared footnote}
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:egr1@pitt.edu}{egr1@pitt.edu}\\
%\phone{+123 (0)123 4445556}
%\fax{+123 (0)123 4445557}

Robert M. Q. Shanks\\
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:shanksrm@pitt.edu}{shanksrm@pitt.edu}\\

Paul W. Leu\\
Benedum Hall, Room 1035 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

\textbf{Corresponding Author:}\\
Paul W. Leu\\
Benedum Hall Room 1035 \\
Pittsburgh, PA, 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

%\bibliographystyle{unsrt}
%\bibliography{AllRefs,LAMPPapers}

\end{document}
